---
title: "Quick Start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Setup 

```{r setup}
# assumes you have client JSON saved to environment argument GAR_CLIENT_JSON
app_project <- googleAuthR::gar_set_client(
  scopes = c("https://www.googleapis.com/auth/cloud-platform"))

library(googleAuthR)
library(googleCloudAutoMLTablesR)
options(googleAuthR.verbose = 0)

gar_auth("gcat.oauth")
```

Test authentication and check in correct project: 

```{r}
# assumes you have projectId string set to environment 
# argument GCAT_PROJECT_ID
projectId <- Sys.getenv("GCAT_PROJECT_ID")

## Get list of locations 
gcat_locations <- gcat_list_locations(projectId = projectId)
gcat_locations$locations
```

## Set location 

```{r}
## manually set location path TODO - @justinjm - update function to handle 
## location setting 
gcat_location <- "us-central1"
gcat_location_path(projectId, gcat_location)
```

## Get list of datasets 

```{r}
gcat_datasets <- gcat_list_datasets(projectId = projectId,
                                    location = gcat_location)
gcat_datasets
```

# Loading data into AutoML Tables 

## Create dataset 
```{r}
# TODO @justinjm - fix function, issue #1 
# https://github.com/justinjm/googleCloudAutoMLTablesR/issues/1  
# gcat_dataset <- gcat_create_dataset(projectId = projectId,
#                                     location = gcat_location,
#                                     displayName = "test_02")
```

## Import data 

### Set dataset 
Create dataset manually in [GCP console](https://console.cloud.google.com/automl-tables/datasets/) `test_dataset`

```{r}
gcat_dataset_display_name <- "test_01"
```

### from GCS 
Setup a GCS bucket that is [regional](https://cloud.google.com/automl-tables/docs/prepare#bucket_requirements) and in `us-central1` region.

```{r}
# gcat_import_data(
#   projectId = projectId,
#   location = gcat_location,
#   dataset_display_name = gcat_dataset_display_name,
#   input_gcs = "gs://gcatr-dev/bank_marketing.csv"
#   )
```

### from BigQuery 

```{r}
gcat_import_data(
  projectId = projectId,
  location = gcat_location,
  dataset_display_name = "test_01_bq",
  # input_source = "bq", # TODO @justinjm - add to function 
  input_gcs = "bq://gc-automl-tables-r.gcatr_dev.bank_marketing"
  )

# view debugging info #
readRDS("request_debug.rds")
```

### Update dataset 

### Create model 

## Modeling 

### Train Model

### Make batch prediction 

### Evaluate predictions 
